WORCS: A Workflow for Open Reproducible Code in Science

### 2020-11-03 paper/reviews_ds.Rmd
Fix function

First, there are several arguments to substantiate the potential for reuse of worcs:

1. WORCS is implemented in an R-package
2. This R-package is available in a standardized repository, namely CRAN ("The Comprehensive R Archive Network")
3. The software meets all criteria of the Core Infrastructure Initiative "best practices" (CII Best Practices)
4. The R-package uses only tools that are fully integrated within the RStudio IDE, thus enhancing ease of use
5. The R-package is compatible with other reproducibility solutions, including Docker, drake, and make

Second, there is some evidence to demonstrate that WORCS is already being adopted (as of 31-10-2020):

1. The preprint has been downloaded 561 times, since being published on 31-05-2020
1. The `worcs` R-package has been downloaded 2401 times from CRAN, since being published on 18-05-2020
1. The GitHub project has been forked by users unknown to us 4 times, and starred (= watched) 32 times
1. The video tutorial for worcs has been viewed 362 times, and liked 18 times (https://www.youtube.com/watch?v=uzjpN_yFeUU)
1. WORCS is used to teach reproducibility at Utrecht University
1. The lead author has given invited lectures on WORCS at the Erasmus University Rotterdam, Eindhoven University of Technology, and Max Planck Institute, Berlin
1. The lead author has applied `worcs` in several research projects:
	* https://github.com/cjvanlissa/storm_meta_father_mother
	* https://github.com/cjvanlissa/veni_sysrev
	* https://github.com/cjvanlissa/placebo_adhd
	* https://github.com/cjvanlissa/schumpe
	* https://github.com/cjvanlissa/coping_covid

Third, although we have not conducted a user evaluation, there is some evidence that `worcs` addresses users' needs:

1. Evaluate worcshops!!
2. The issues page on the worcs GitHub profile demonstrates that we have been very responsive in addressing users' feedback (as required by the aforementioned CII Best Practices):
* https://github.com/cjvanlissa/worcs/issues?q=is%3Aissue+is%3Aclosed

@@

Response: In addressing this comment, we respectfully refer to our response to the preceding comment ("There is no user evaluation", R1), and again emphasize the Editor's comment that "resource papers do not need to have a full-blown user evaluation". We would also like to clarify that the goal of the present manuscript is to define the problem WORCS intends to address (specifically; meeting the TOP-guidelines for Open Science), introduce the tools WORCS uses to address this problem, explain how WORCS uses these tools, and provide a step-by-step workflow. It is not clear what "claims" are made that are unsupported by evidence. In the revision, we have attempted to further clarify this goal from the paper onset: REF.

We do take the suggestion of performing a user evaluation very seriously, but in our mind, this is a next step. We have built WORCS based on established tools and best practices, and we have gathered preliminary positive feedback from the community through workshops and teaching.

@@

Response: We understand that our writing comes across as contradictory,
and this apparent contradiction arises from a lack of explicit definitions of the terms "replication" and "reproducibility" in the original manuscript.
We are aware of the oft-lamented lack of consistent definitions for these terms (e.g., Patil, Peng, & Leek, 2019; Plesser, 2018).
In the revision, we have attempted to address this lack of clarity by including explicit definitions for these terms:

@@

<!--
check_urls <- function(x){
  #x = "C:/Git_Repositories/worcs/paper/manuscript_ds.Rmd"
  txt <- readLines(x)
  mtch <- regmatches(txt,regexpr("(http[^ ]*)|(ftp[^ ]*)|(www\\.[^ ]*)",txt))
  mtch <- gsub("[\\)\\.,;]+$", "", mtch)
  #out <- sapply(mtch, RCurl::url.exists)
  out <- sapply(mtch, httr::http_error)
}
-->

>>>>

First, there are several arguments to substantiate the potential for reuse of worcs:
1) Worcs is implemented in an R-package
2) This R-package is available in a standardized repository, namely CRAN ("The Comprehensive R Archive Network")
3) The software meets all criteria of the Core Infrastructure Initiative "best practices" (CII Best Practices)
4) The R-package uses only tools that are fully integrated within the RStudio IDE, thus enhancing ease of use
5) The R-package is compatible with other reproducibility solutions, including Docker, drake, and make

Second, there is some evidence to demonstrate that worcs is already being adopted (as of 31-10-2020):

Third, although we have not conducted a user evaluation, there is some evidence that worcs addresses users' needs:
1) Evaluate worcshops!!
2) The issues page on the worcs GitHub profile demonstrates that we have been very responsive in addressing users' feedback (as required by the aforementioned CII Best Practices):
* https://github.com/cjvanlissa/worcs/issues?q=is%3Aissue+is%3Aclosed

@@

Response: In addressing this comment, we respectfully refer to our response to the preceding comment ("There is no user evaluation", R1), and again emphasize the Editor's comment that "resource papers do not need to have a full-blown user evaluation". We would also like to clarify that the goal of the present manuscript is to define the problem worcs intends to address (specifically; meeting the TOP-guidelines for Open Science), introduce the tools worcs uses to address this problem, explain how worcs uses these tools, and provide a step-by-step workflow. It is not clear what "claims" are made that are unsupported by evidence. In the revision, we have attempted to further clarify this goal from the paper onset: REF.

We do take the suggestion of performing a user evaluation very seriously, but in our mind, this is a next step. First, the workflow must be published, then it can be taught, and subsequently evaluated.

@@

Response: We understand that our writing comes across as contradictory,
and this apparent contradiction arises from a lack of explicit definitions of the terms "replication" and "reproducibility" in the original manuscript.
We are aware of the oft-lamented lack of consistent definitions for these terms (e.g., Patil, Peng, & Leek, 2019; Plesser, 2018).
In the Revision, we have attempted to address this lack of clarity by including explicit definitions for these terms:

@@

<!--
check_urls <- function(x){
  #x = "C:/Git_Repositories/worcs/paper/manuscript_ds.Rmd"
  txt <- readLines(x)
  mtch <- regmatches(txt,regexpr("(http[^ ]*)|(ftp[^ ]*)|(www\\.[^ ]*)",txt))
  mtch <- gsub("[\\)\\.,;]+$", "", mtch)
  #out <- sapply(mtch, RCurl::url.exists)
  out <- sapply(mtch, httr::http_error)
  out
}
-->
